Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-02 response/response.tex

We define floss-refactoring before in the paragraph
as you can see below. Regarding the methodology to detect floss-refactorings, 
we manually inspected all the cases to ensure that 
floss-refactorings were not being considered.

\begin{quote}
    The same approach is used to analyze the impact of regular 
    changes. Security patches can be performed through one commit (single-commit); 
    several consecutive commits (multi-commits); or, commit(s) interleaved with more 
    programming activities (floss-refactoring). Only $10.7\%$ of the data points 
    of our dataset involve more than one commit, the other
    $89.3\%$ of the cases are single-commit patches. We manually 
    inspected all the cases and identified $23$ floss-refactorings. 
    These were disregarded since it would not be fair to measure the 
    maintainability of these cases where other programming activities 
    are involved.
\end{quote}

\begin{revcomment}[2.14]
    Section 3\\
    \begin{itemize}
        \item Page 11, Line 42 - I think you are saying you removed these two guidelines 
        from the analysis of all projects (as shown in Figure 4) but this paragraph seems 
        to say this was only for projects with large code bases.
    \end{itemize}
\end{revcomment}

\Us Yes, we started with all the guidelines but after analyzing the BCH results 
we found that some of the results of the \emph{Keep Your Codebase Small} guidelines were not viable
because they retrieved values above the limit set by BCH ($20$ Person-years). We did not want 
to lose more data points. Thus, we decided to not consider the guideline for all projects.

We also did not consider the \emph{Automated Tests} guideline because
this guideline does not contemplate vulnerability scanning and penetration testing
which are the two most important testing techniques in security.

We improved the paper in the following text:

\begin{quote}
    For projects with large codebases, the results retrieved for 
\emph{Keep Your Codebase Small} were not viable because they 
retrieved values above the limit set by BCH ($20$ Person-years). Thus, 
we decided to not consider this guideline in our research. The 
\emph{Automated Tests} guideline was also not considered since the 
tool does not contemplate two of the most important techniques to 
security testing: vulnerability scanning and penetration testing. 
\end{quote}

### 2021-02-02 response/response.tex

We would like to rebut your concern on the tools and 
metrics we are using. As we explained previously, in comment 1.1, 
BCH checks GitHub codebases against 10 maintainability guidelines 
as devised by Software Improvement Group (SIG). SIG has devised 
these guidelines after many years of experience: analyzing more 
than 15 million lines of code every week, SIG maintains the industry’s largest 
benchmark, containing more than 10 billion lines of code across 200+ technologies; SIG 
is the *only* lab in the world certified by TÜViT to issue ISO 25010:2011 
certificates\footnote{Information available here: 
\url{https://www.softwareimprovementgroup.com/methodologies/iso-iec-25010-2011-standard/}}
The guidelines and their relation to maintainability is well 
detailed in the SIG's book ``Building Maintainable 
Software: Ten Guidelines for Future-Proof Code''
\footnote{Available here: \url{https://www.softwareimprovementgroup.com/resources/ebook-building-maintainable-software/}}.

Note, that our goal is to measure the impact of security patches on software 
maintainability and not finding vulnerabilities---vulnerabilities
are already identified and located. Thus, for now, 
we do not need to leverage static analysis tools.

For future research, it is indeed interesting to 
understand how BCH can be fused with a static analysis tool 
and how the BCH results can help 
security engineers assess the risk of their patches and guide 
them on performing better patches. But for now we only try
to understand the impact of security patches on those metrics.

All in all, we argue that BCH is appropriate 
to perform the current analysis.

@@

\begin{revcomment}[2.4]

    Intro:\\
    You should check out this paper: 
    Li, Frank and Paxson, Vern. A large-scale empirical study of security patches.
    ACM SIGSAC Conference on Computer and Communications Security in 2017.

\end{revcomment}

\Us Thank you for bringing our attention to this paper. We now discuss
this paper in the Related Work section and used it to support some 
of our claims and findings.

@@

\begin{quote}
    Security patches can be performed through one commit, 
several consecutive commits, or commit(s) interleaved with more 
programming activities (floss-refactoring). This study considers 
mainly single-commit patches. Yet, a small percentage of data points 
had more than one commit involved in the patch. We manually 
inspected these cases and $23$ floss-refactorings were identified 
and disregarded since it would not be fair to measure the 
maintainability of these cases where other programming activities 
are involved.

For projects with large codebases, the results retrieved for 
\emph{Keep Your Codebase Small} were not viable because they 
retrieved values above the limit set by BCH ($20$ Person-years). The 
\emph{Automated Tests} guideline was also not considered since the 
tool does not contemplate two of the most important techniques to 
security testing: vulnerability scanning and penetration testing. 
Instead, it only contemplates unit testing. Due to BCH limitations, 
we detected a few data points that retrieved incorrect overall 
calculations. Those data points were disregarded from the study.
\end{quote}

Those are the cases that were tossed from the initial $1300$ patches.

Regarding the second question:
while manually inspecting the patches, we were not able to map
the issues to any CWE ID due to the lack of information on the 
problem and solution. Yet, we manually validated the list again and after discussion 
we classified more $40$ cases. We also clarified this on the paper:

@@

We define floss-refactoring before in the paragraph
as you can see below. Regarding the methodology to detect floss-refactorings, 
we manually inspected all the cases to ensure that 
floss-refactorings were not being considered.

\begin{quote}
    The same approach is used to analyze the impact of regular 
    changes. Security patches can be performed through one commit (single-commit); 
    several consecutive commits (multi-commits); or, commit(s) interleaved with more 
    programming activities (floss-refactoring). Only $10.7\%$ of the data points 
    of our dataset involve more than one commit, the other
    $89.3\%$ of the cases are single-commit patches. We manually 
    inspected all the cases and identified $23$ floss-refactorings. 
    These were disregarded since it would not be fair to measure the 
    maintainability of these cases where other programming activities 
    are involved.
\end{quote}

\begin{revcomment}[2.14]
    Section 3\\
    \begin{itemize}
        \item Page 11, Line 42 - I think you are saying you removed these two guidelines 
        from the analysis of all projects (as shown in Figure 4) but this paragraph seems 
        to say this was only for projects with large code bases.
    \end{itemize}
\end{revcomment}

\Us We started with all the guidelines but after analyzing the BCH results 
we found that some of the results of the \emph{Keep Your Codebase Small} guidelines were not viable
because they retrieved values above the limit set by BCH ($20$ Person-years). We did not want 
to lose more data points. Thus, we decided to not consider the guideline for all projects.

### 2021-02-02 response/response.tex

\begin{quote}
    Security patches can be performed through one commit, 
several consecutive commits, or commit(s) interleaved with more 
programming activities (floss-refactoring). This study considers 
mainly single-commit patches. Yet, a small percentage of data points 
had more than one commit involved in the patch. We manually 
inspected these cases and $23$ floss-refactorings were identified 
and disregarded since it would not be fair to measure the 
maintainability of these cases where other programming activities 
are involved.

For projects with large codebases, the results retrieved for 
\emph{Keep Your Codebase Small} were not viable because they 
retrieved values above the limit set by BCH ($20$ Person-years). The 
\emph{Automated Tests} guideline was also not considered since the 
tool does not contemplate two of the most important techniques to 
security testing: vulnerability scanning and penetration testing. 
Instead, it only contemplates unit testing. Due to BCH limitations, 
we detected a few data points that retrieved incorrect overall 
calculations. Those data points were disregarded from the study.
\end{quote}

Those are the cases that were tossed from the initial $1300$ patches.

Regarding the second question:
while manually inspecting the patches, we were not able to map
the issue to any CWE with confidence due to the lack of quality
information on the vulnerability/patch. We clarified this in the paper.

### 2021-02-02 paper/emse20.tex
2.18
some fixes

In this study, we focus on computing the maintainability of the 
commits before and after the security patching to evaluate if its 
impact was positive, negative or none. The $1300$ patches in the 
dataset were analyzed using the BCH toolset to calculate their 
maintainability reports. Due to the limitations of BCH (in particular, 
lack of language support and project size) and the presence of
floss-refactorings, $331$ patches were tossed---explained in 
more detail in Section~\ref{sec:main_analysis}.
The final dataset used in this 
paper comprises $969$ security patches from $260$ projects. We used the 
Common Weakness Enumeration (CWE) taxonomy to classify each vulnerability. 
For instance,  the \texttt{Fix CVE-2014-1608: mc\_issue\_attachment\_get SQL injection} 
(\texttt{00b4c17}\footnote{CVE-$2014$-$1608$ details available at 
\url{https://github.com/mantisbt/mantisbt/commit/00b4c17088fa56594d85fe46b6c6057bb3421102} 
(Accessed on \today)}) is a \emph{CWE-89: Improper Neutralization of Special Elements used 
in an SQL Command ('SQL Injection')}\footnote{CWE-$89$ details available at \url{https://cwe.mitre.org/data/definitions/89.html} 
(Accessed on \today)} according to the CWE taxonomy.
We were able to classify a total of $906$ patches using the CWE taxonomy:
the CWE's for $536$ patches were automatically scraped from the National 
Vulnerability Dataset (NVD); while the other $370$ patches were manually classified by 
the authors following the \emph{Research Concepts} CWE's list. A total 
of $63$ patches were not classified because we were not able to map
the issues to any CWE ID due to the lack of quality information on the 
problem and solution.

@@

In this research, we follow a very similar methodology to the one 
presented in previous work on the maintainability of energy-oriented 
fixes~\cite{8919169}. The inner-workings of BCH were proposed
originally in 2007~\cite{4335232} and suffer refinements later~\cite{5609747,6113040,baggen2012}. 
As said before, the web-based source code 
analysis service \emph{Better Code Hub} (BCH) is used to collect the 
maintainability reports of the patches of each project. 
Table~\ref{tab:guidelines} presents the $10$ guidelines proposed
by BCH's authors for delivering software that is not difficult to
maintain~\cite{Visser:2016:OREILLY} and, maps each guideline to the 
metric calculated by BCH. Theses guidelines are calculated using the 
metrics presented in~\cite{criteria:2017} and are also briefly 
explained on Table~\ref{tab:guidelines}. 
During each guideline evaluation, the tool determines the compliance 
towards one guideline by establishing limits for the percentage of 
code allowed to be in each of the $4$ risk severity levels
(\emph{low risk}, \emph{medium risk}, \emph{high risk}, and 
\emph{very high risk}). If the project does not violate those 
thresholds, then the BCH considers that the code is compliant with 
a guideline. These thresholds are determined by BCH using their own
data/experience---using open-source and closed software systems. If 
a project is compliant with a guideline, it means that it is at 
least $65\%$ better than the software used by BCH to calculate the 
thresholds\footnote{Check the answer to \emph{How can I adjust the 
threshold for passing/not passing a guideline?} at
\url{https://bettercodehub.com/docs/faq} (Accessed on \today{})}.

@@

For projects with large codebases, the results retrieved for 
\emph{Keep Your Codebase Small} were not viable because they 
retrieved values above the limit set by BCH ($20$ Person-years). The 
\emph{Automated Tests} guideline was also not considered since the 
tool does not contemplate two of the most important techniques to 
security testing: vulnerability scanning and penetration testing. 
Instead, it only contemplates unit testing. Due to BCH limitations, 
we detected $308$ data points that retrieved incorrect overall 
calculations. Those data points were disregarded from the study.

>>>>

In this study, we focus on computing the maintainability of the 
commits before and after the security patching to evaluate if its 
impact was positive, negative or none. The $1300$ patches in the 
dataset were analyzed using the BCH toolset to calculate their 
maintainability reports. Due to the limitations of BCH (in particular, 
lack of language support and project size) and the presence of
floss-refactorings, $331$ patches were tossed---explained in 
more detail in Section~\ref{sec:main_analysis}.
The final dataset used in this 
paper comprises $969$ security patches from $260$ projects. We used the 
Common Weakness Enumeration (CWE) taxonomy to classify each vulnerability. 
For instance,  the \texttt{Fix CVE-2014-1608: mc\_issue\_attachment\_get SQL injection} 
(\texttt{00b4c17}\footnote{CVE-$2014$-$1608$ details available at 
\url{https://github.com/mantisbt/mantisbt/commit/00b4c17088fa56594d85fe46b6c6057bb3421102} 
(Accessed on \today)}) is a \emph{CWE-89: Improper Neutralization of Special Elements used 
in an SQL Command ('SQL Injection')}\footnote{CWE-$89$ details available at \url{https://cwe.mitre.org/data/definitions/89.html} 
(Accessed on \today)} according to the CWE taxonomy.
We were able to classify a total of $906$ patches using the CWE taxonomy:
the CWE's for $536$ patches were automatically scraped from the National 
Vulnerability Dataset (NVD); while the other $370$ patches were manually classified by 
the authors following the \emph{Research Concepts} CWE's list. A total 
of $63$ patches were not classified because we were not able to map
the issue to any CWE with confidence due to the lack of quality
information on the vulnerability/patch.

@@

In this research, we follow a very similar methodology to the one 
presented in previous work on the maintainability of energy-oriented 
fixes~\cite{8919169}. The inner-workings of BCH were proposed
originally in 2007~\cite{4335232} and suffered refinements later~\cite{5609747,6113040,baggen2012}. 
As said before, the web-based source code 
analysis service \emph{Better Code Hub} (BCH) is used to collect the 
maintainability reports of the patches of each project. 
Table~\ref{tab:guidelines} presents the $10$ guidelines proposed
by BCH's authors for delivering software that is not difficult to
maintain~\cite{Visser:2016:OREILLY} and, maps each guideline to the 
metric calculated by BCH. Theses guidelines are calculated using the 
metrics presented in~\cite{criteria:2017} and are also briefly 
explained on Table~\ref{tab:guidelines}. 
During each guideline evaluation, the tool determines the compliance 
towards one guideline by establishing limits for the percentage of 
code allowed to be in each of the $4$ risk severity levels
(\emph{low risk}, \emph{medium risk}, \emph{high risk}, and 
\emph{very high risk}). If the project does not violate those 
thresholds, then the BCH considers that the code is compliant with 
a guideline. These thresholds are determined by BCH using their own
data/experience---using open-source and closed software systems. If 
a project is compliant with a guideline, it means that it is at 
least $65\%$ better than the software used by BCH to calculate the 
thresholds\footnote{Check the answer to \emph{How can I adjust the 
threshold for passing/not passing a guideline?} at
\url{https://bettercodehub.com/docs/faq} (Accessed on \today{})}.

@@

For projects with large codebases, the results retrieved for 
\emph{Keep Your Codebase Small} were not viable because they 
retrieved values above the limit set by BCH ($20$ Person-years). Thus, 
we decided to not consider this guideline in our research. The 
\emph{Automated Tests} guideline was also not considered since the 
tool does not contemplate two of the most important techniques to 
security testing: vulnerability scanning and penetration testing. 
Instead, it only contemplates unit testing. Due to BCH limitations, 
we detected $308$ data points that retrieved incorrect overall 
calculations. Those data points were disregarded from the study.
